\documentclass[pdf, aspectratio=169, 12pt]{beamer}
\usepackage[]{hyperref, graphicx, siunitx, lmodern, tikz, booktabs, physics, multicol}
\usepackage[mode=buildnew]{standalone}
\usepackage{pdfpc-commands}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}

\usetheme{Python}

\graphicspath{ {Images/} }

\sisetup{per-mode=symbol}
\usetikzlibrary{calc, patterns, decorations.markings, decorations.pathmorphing, shapes, fit}

%Preamble
\title{Digital Dodgeball}
\author{Jed Rembold}
\date{April 24, 2020}

\begin{document}

\begin{frame}{Announcements}
	\begin{itemize}
		\item Grading
			\begin{itemize}
				\item Plugging away. Hoping to have the midterm projects finished by the end of the weekend
				\item I'll post and updated grade report as soon as I finish those.
			\end{itemize}
		\item No class next week! Just working on your projects!
		\item I'll post links each class day where you can find me to ask questions if you need help or advice
		\item Polling: \nolinkurl{rembold-class.ddns.net}
	\end{itemize}
\end{frame}

\begin{frame}{Group Project Info}
		\begin{itemize}
			\item Emails with group assignments should have gone out. Start thinking through and talking what you want to create as a group!
			\item Still working on getting the shared repositories made. Will be trying to get that done during ``lab'' today
			\item Let me know if you are looking for ideas or want to bounce some ideas off me!
			\item If you are trying to judge if there is enough content in your project, a rough rule of thumb would be to ask yourself if there is between 1-2 homework assignments worth of work for each group member
			\item Try to aim to have your idea for your project mapped out by the end of of the weekend (and maybe let me know what it is)
		\end{itemize}
\end{frame}

\begin{frame}[fragile]{Polling Question}
	Where are groups generally at with respect to planning?
	\begin{poll}
		\item We have met and talked about some ideas, but not settled on something
		\item We have generally come to a concensus about what we want to do
		\item We haven't gotten a chance to get together and discuss yet
		\item We have group projects?
	\end{poll}
\end{frame}

\begin{frame}{Getting started with Digital Dodgeball}
	\begin{itemize}
		\item Can get materials at: \link{https://github.com/jrembold/WUPhys-CodeComp/archive/release.zip}{https://github.com/jrembold/WUPhys-CodeComp/archive/release.zip}
			\vspace{5mm}

		\item Documentation at: \link{https://jrembold.github.io/WUPhys-CodeComp/documentation/}{https://jrembold.github.io/WUPhys-CodeComp/documentation/}
	\end{itemize}
\end{frame}

\begin{frame}{General Description}
	\begin{itemize}
		\item A simultaneous turn-based game of dodgeball
		\item You write a \alert{script} to control your player. You have no direct control.
		\item Only 5 possible moves to make each round, and you can only do 1
		\item You will receive a new batch of information each round about what your player can ``see'' to base your next rounds move off of
	\end{itemize}
\end{frame}

\begin{frame}{The Pieces}
	\begin{itemize}
		\item The Server
			\begin{itemize}
				\item What actually runs the game
				\item All code here is written already, you just need to run it to play a game
			\end{itemize}
		\item The Visualizer
			\begin{itemize}
				\item Visualizes the game so you can see what happened (or what went wrong)
				\item Has both Matplotlib and Tkinter interfaces
				\item Shown by default upon conclusion of any server game
			\end{itemize}
		\item The player script(s)
			\begin{itemize}
				\item The part you actually write!
				\item Has some boilerplate code that has to be there, but the rest is up to you!
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Running a Server}
	\begin{itemize}
		\item Can launch from either a normal terminal window or from within a Python terminal
		\item Has several options you can/need to provide, the most important of which is the \pyi{-i} flag, after which follows a list of the player scripts you want in the game.
			\begin{pythoncode}
				python server.py -i RandomMan.py SimpleMan.py
			\end{pythoncode}
			or
			\begin{pythoncode}
				run server.py -i RandomMan.py SimpleMan.py
			\end{pythoncode}
	\end{itemize}
\end{frame}

\begin{frame}{Writing your Player Script}
	\begin{itemize}
		\item Template provided with the necessary basics
		\item Always need to send one command to the server each round:
			\begin{itemize}
				\item \pyi{'forward'}: Go forward one space
				\item \pyi{'rotCW'}: Rotate 90 degrees clockwise
				\item \pyi{'rotCCW'}: Rotate 90 degrees counter-clockwise
				\item \pyi{'ball'}: Throws a dodgeball in the direction the player is facing
				\item \pyi{'ping'}: Take a turn to get more info on surroundings
			\end{itemize}
		\item Use \pyi{bot.sendMessage( )} to send the message to the server
	\end{itemize}
\end{frame}

\begin{frame}{Gathering Info}
	\begin{itemize}
		\item Should use \pyi{bot.getMapState()} each iteration to get latest intel
		\item Map information stored as attributes of \pyi{bot}
			\begin{itemize}
				\item \pyi{.active}: Has your bot been disqualified?
				\item \pyi{.playercount}: How many players are still in the game?
				\item \pyi{.ballcount}: How many dodgeballs does your player currently hold?
				\item \pyi{.vision}: Looking forwards, a list of what your player ``sees''
				\item \pyi{.lastping}: Dictionary of all info from most recent ping
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{What do you see?}
	\begin{itemize}
		\item Numbers correspond to different objects in vision:
			\begin{itemize}
				\item 0 - Nothing here. Empty space.
				\item 1 - Wall here. Vision ends at a wall, so you shouldn't see this.
				\item 2 - Active (moving) dodgeball. Decimal indicates direction
				\item 3 - Inactive (fallen) dodgeball.
				\item 50+ - Id for player. Decimal indicates facing direction.
			\end{itemize}
		\item Decimals indicate facing/traveling direction:
			\begin{itemize}
				\item 0.0 - Facing North
				\item 0.1 - Facing East
				\item 0.2 - Facing South
				\item 0.3 - Facing West
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{General Tips}
	\begin{itemize}
		\item If you remain in one space for 120 turns (even if you are rotating each turn) you will be disqualified.
		\item The map starts to close in slowly and then increasingly rapidly as the game progresses
		\item Touching someone in front of you will also disqualify them
		\item Players can disqualify each other simultaneously
	\end{itemize}
\end{frame}









\end{document}

